Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-04 neurips-20/cvx-flats.tex
Sec 4 pass.  Just unsure how to rephrase one sentence

\btw{TODO: Give readers a sense of difficulty; add a little discussion}
We now state our lower bound.

@@

	\btw{Bo: moved all $\ell$ stuff later.}
	Let $\Gamma := \prop{L}$ and suppose $(L, \psi)$ indirectly elicits $\gamma$.
	By definition of a property, there is some $u \in \Gamma(p)$.
	We will first show $F \cap \simplex \subseteq \Gamma_u$.

	As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p} \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.
  % (Observe that in order for $L$ to be convex, $L(\cdot, y)$ must be convex for all $y \in \Y$.) 
	Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y : x_y \in \partial L(u,y) \; \forall y\in\Y\}$.
	Defining the matrix $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$, we have $W p = \sum_y p_y x_y = \vec 0$;
  cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
	Now taking $F := \ker(W) \cap \affhull(\simplex)$ (by Definition~\ref{def:flat}), we have $\codim(F) = \rank(W) \leq d$, and $p \in F$ by construction.
	%% Bo: the below sentence seemed to bring in gamma_r too early. Saved that for later. June 3 10pm
	To see $F \cap \simplex \subseteq \Gamma_u$, from the chain of equivalences above, we have for any $q\in\simplex$ that $q \in \ker W \implies u \in \Gamma(q) \implies q \in \Gamma_u$.

@@

The proof takes its insipration from~\citet[Theorem 16]{ramaswamy2016convex}, and extracts a witness $W$ of the optimality of a surrogate prediction $u$.
This witness $W$ takes the form of a matrix whose columns are selection of subgradients of $L$, and thus $u$ must also be optimal for any other distribution in the flat defined by the kernel of $W$.
As we show next, the original statement of~\citet[Theorem 16]{ramaswamy2016convex}, which uses the stronger notion of calibration and thus applies only to discrete target losses, actually follows as a special case of Theorem~\ref{thm:cvx-flats}.

>>>>

We now state our lower bound.

@@

	Let $\Gamma := \prop{L}$ and suppose $(L, \psi)$ indirectly elicits $\gamma$.
	By definition of a property, there is some $u \in \Gamma(p)$.
	We will first show $F \cap \simplex \subseteq \Gamma_u$.

	As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p} \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.
  % (Observe that in order for $L$ to be convex, $L(\cdot, y)$ must be convex for all $y \in \Y$.) 
	Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y : x_y \in \partial L(u,y) \; \forall y\in\Y\}$.
	Defining the matrix $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$, we have $W p = \sum_y p_y x_y = \vec 0$;
  cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
	Now taking $F := \ker(W) \cap \affhull(\simplex)$, we have $\codim(F) = \rank(W) \leq d$ by Definition~\ref{def:flat}, and $p \in F$ by construction.
	%% Bo: the below sentence seemed to bring in gamma_r too early. Saved that for later. June 3 10pm
	To see $F \cap \simplex \subseteq \Gamma_u$, from the chain of equivalences above, we have for any $q\in\simplex$ that $q \in \ker W \implies u \in \Gamma(q) \implies q \in \Gamma_u$.

@@

The proof takes its insipration from~\citet[Theorem 16]{ramaswamy2016convex}, and extracts a witness $W$ of the optimality of a surrogate prediction $u$.
This witness $W$ takes the form of a matrix whose columns are selection of subgradients of $L$, and thus $u$ must also be optimal for any other distribution in the flat defined by the kernel of $W$.
As we show next, the original statement of~\citet[Theorem 16]{ramaswamy2016convex}, which uses the stronger notion of calibration and thus applies only to discrete target losses, actually follows as a special case of Theorem~\ref{thm:cvx-flats}. \jessiet{How to rephrase this?}
